---
title: "Ad Trafficking Setup with rdfp"
author: "Steven M. Mortimer"
date: "2018-03-29"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 4
    keep_md: true
vignette: >
  %\VignetteIndexEntry{Availability and Reporting with rdfp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
NOT_CRAN <- identical(tolower(Sys.getenv("NOT_CRAN")), "true")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  purl = NOT_CRAN,
  eval = NOT_CRAN
)
```

First, we load `dplyr` and `lubridate` to use in this vignette along with loading 
the `rdfp` package and specifying the DFP network we would like to connect to. 

```{r load-package}
suppressWarnings(suppressMessages(library(dplyr)))
suppressWarnings(suppressMessages(library(lubridate)))
library(rdfp)
options(stringsAsFactors = FALSE)
options(rdfp.network_code = 123456789)
```

Just a note, that it's not necessary to setup your own application client_id and 
client_secret through the Google Developer's Console. The only difference is that 
the authentication will be run through the client created and associated with the 
`rdfp` package. By using the package client, you will *NOT* be giving access to 
your DFP to anyone, the package is just the medium for you to connect to 
your own data. If you wanted more control you would specify those options like so: 

```{r other-params, eval=FALSE}
options(rdfp.application_name = "MyApp")
options(rdfp.client_id = "012345678901-99thisisatest99.apps.googleusercontent.com")
options(rdfp.client_secret = "Th1s1sMyC1ientS3cr3t")

dfp_auth()
```

```{r auth, include = FALSE}
## I grab the token from the testing directory because that's where it is to be
## found on Travis
token_path <- file.path("..", "tests", "testthat", "rdfp_token.rds")
suppressMessages(dfp_auth(token = token_path, verbose = FALSE))
options_path <- file.path("..", "tests", "testthat", "rdfp_options.rds")
rdfp_options <- readRDS(options_path)
options(rdfp.network_code = rdfp_options$test_network_code)
```

#### Setup Custom Labels for Items

Custom labels are helpful for "tagging" DFP items with metadata
that can later be used frequency capping, doing competitive exclusion or 
other specific actions. See the following link for Google's explanation on their uses: 
(https://support.google.com/dfp\_premium/answer/190565?hl=en&ref_topic=30224)

```{r, eval=FALSE}
# this creates a label called "Last Minute Change" that we can add
# to any line item or order that we felt deserved this label.
request_data <- data.frame(name="auto - competitive exclusion", 
                           description=paste0("A label to prevent two different car ",
                                              "companies from showing ads together"), 
                           types='COMPETITIVE_EXCLUSION')
dfp_createLabels_result <- dfp_createLabels(request_data)
```

#### Setup Custom Fields for Items

Custom fields are helpful for "tagging" DFP items with metadata
that can later be used filtering or reporting. See the following link for 
Google's explanation on their uses: (https://support.google.com/dfp\_premium/answer/2694303?hl=en)

```{r, eval=FALSE}
# this creates an extra field on the USER entity type that denotes what shift 
# the user works during the day. First we create the field, then populate
# with potential options since it is a dropdown field.
request_data <- data.frame(name='Shift',
                           description='The shift that this user usually works.', 
                           entityType='USER',
                           dataType='DROP_DOWN',
                           visibility='FULL')
dfp_createCustomFields_result <- dfp_createCustomFields(request_data)

request_data <- data.frame(customFieldId=rep(dfp_createCustomFields_result$id, 3),
                           displayName=c('Morning', 'Afternoon', 'Evening'))
dfp_createCustomFieldOptions_result <- dfp_createCustomFieldOptions(request_data)
```

#### Setup Custom Targeting Keys and Values

DFP allows traffickers to create custom tags to better target line items on their site.
For example, a certain section of the site or search term used by a visitor can be 
encoded as custom targeting keys and values that can later be used when creating 
orders and line items, and evaluating potential inventory. See the following link for 
Google's explanation on their uses: (https://support.google.com/dfp\_premium/answer/188092?hl=en)

```{r}
# create the key
request_data <- list(keys=list(name='Test1', 
                               displayName='TestKey1', 
                               type='FREEFORM'))
dfp_createCustomTargetingKeys_result <- dfp_createCustomTargetingKeys(request_data)
dfp_createCustomTargetingKeys_result

# create the values
request_data <- data.frame(customTargetingKeyId=rep(dfp_createCustomTargetingKeys_result$id,2),
                           name=c('TestValue1','TestValue2'), 
                           displayName=c('TestValue1','TestValue2'), 
                           matchType=rep('EXACT', 2))
dfp_createCustomTargetingValues_result <- dfp_createCustomTargetingValues(request_data)
dfp_createCustomTargetingValues_result
```

```{r cleanup, include = FALSE}
  request_data <- list(customTargetingValueAction='DeleteCustomTargetingValues',
                       filterStatement=list('query'="WHERE name like 'Test%'"))
  res <- dfp_performCustomTargetingValueAction(request_data, as_df=FALSE)

  request_data <- list(customTargetingKeyAction='DeleteCustomTargetingKeys',
                       filterStatement=list('query'="WHERE name='Test1'"))
  res <- dfp_performCustomTargetingKeyAction(request_data, as_df=FALSE)
```