---
title: "Administrative Tasks with rdfp"
author: "Steven M. Mortimer"
date: "2018-03-29"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 4
    keep_md: true
vignette: >
  %\VignetteIndexEntry{Availability and Reporting with rdfp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
NOT_CRAN <- identical(tolower(Sys.getenv("NOT_CRAN")), "true")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  purl = NOT_CRAN,
  eval = NOT_CRAN
)
```

First, we load `dplyr` and `lubridate` to use in this vignette along with loading 
the `rdfp` package and specifying the DFP network we would like to connect to. 

```{r load-package}
suppressWarnings(suppressMessages(library(dplyr)))
suppressWarnings(suppressMessages(library(lubridate)))
library(rdfp)
options(stringsAsFactors = FALSE)
options(rdfp.network_code = 123456789)
```

Just a note, that it's not necessary to setup your own application client_id and 
client_secret through the Google Developer's Console. The only difference is that 
the authentication will be run through the client created and associated with the 
`rdfp` package. By using the package client, you will *NOT* be giving access to 
your DFP to anyone, the package is just the medium for you to connect to 
your own data. If you wanted more control you would specify those options like so: 

```{r other-params, eval=FALSE}
options(rdfp.application_name = "MyApp")
options(rdfp.client_id = "012345678901-99thisisatest99.apps.googleusercontent.com")
options(rdfp.client_secret = "Th1s1sMyC1ientS3cr3t")

dfp_auth()
```

```{r auth, include = FALSE}
token_path <- file.path("..", "tests", "testthat", "rdfp_token.rds")
suppressMessages(dfp_auth(token = token_path, verbose = FALSE))
options_path <- file.path("..", "tests", "testthat", "rdfp_options.rds")
rdfp_options <- readRDS(options_path)
options(rdfp.network_code = rdfp_options$network_code)
```

#### Check Current User Info

```{r}
# Check current user or network
user_info <- dfp_getCurrentUser()
user_info[,c('id', 'isActive')]
network_info <- dfp_getCurrentNetwork()
network_info[,c('id', 'networkCode')]
```

#### Create Team and Users

```{r, eval=FALSE}
# create a team and user and add the user to that team

#first create the team
request_data <- list(teams=list(name="TestTeam1", 
                                description='API Test Team 1', 
                                hasAllCompanies='true', 
                                hasAllInventory='true',
                                teamAccessType='READ_WRITE'))
dfp_createTeams_result <- dfp_createTeams(request_data)

# second create the user
request_data <- data.frame(name = paste0("TestUser", 1:3),
                           email = paste0('testuser', 1:3, '@gmail.com'), 
                           roleId = rep(-1, 3))
dfp_createUsers_result <- dfp_createUsers(request_data)

# third associate the user to that team
request_data <- data.frame(teamid=rep(dfp_createTeams_result$id, 3),
                           userid=dfp_createUsers_result$id)
dfp_createUserTeamAssociations_result <- dfp_createUserTeamAssociations(request_data)

# Note: User roleId = -1 is the Administrative role
# use dfp_getAllRoles() to view other options

# Creating custom roles is a premium feature, which
# small business accounts won't have and creating the roles 
# can only be done from the user interface, not the API.
```

#### Create Companies and Contacts

```{r eval = FALSE}
# create a company and add a contact to it

# first create the company
request_data <- list(companies=list(name="TestCompany1", 
                                    type='HOUSE_ADVERTISER', 
                                    address='123 Main St Hometown, FL USA', 
                                    email='testcompany1@gmail.com', 
                                    comment='API Test'))
dfp_createCompanies_result <- dfp_createCompanies(request_data)

# second create the contact and specify the companyId
request_data <- list(contacts=list(name="TestContact1", 
                                    companyId=dfp_createCompanies_result$id, 
                                    status='UNINVITED', 
                                    cellPhone='(888) 999-7777',
                                    comment='API Test', 
                                    email='testcontact1@gmail.com'))
dfp_createContacts_result <- dfp_createContacts(request_data)
```
