---
title: "Manipulating Orders and LineItems with rdfp"
author: "Steven M. Mortimer"
date: "2018-03-29"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 4
    keep_md: true
vignette: >
  %\VignetteIndexEntry{Availability and Reporting with rdfp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
NOT_CRAN <- identical(tolower(Sys.getenv("NOT_CRAN")), "true")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  purl = NOT_CRAN,
  eval = NOT_CRAN
)
```

First, we load `dplyr` and `lubridate` to use in this vignette along with loading 
the `rdfp` package and specifying the DFP network we would like to connect to. 

```{r load-package}
suppressWarnings(suppressMessages(library(dplyr)))
suppressWarnings(suppressMessages(library(lubridate)))
library(rdfp)
options(stringsAsFactors = FALSE)
options(rdfp.network_code = 123456789)
```

Just a note, that it's not necessary to setup your own application client_id and 
client_secret through the Google Developer's Console. The only difference is that 
the authentication will be run through the client created and associated with the 
`rdfp` package. By using the package client, you will *NOT* be giving access to 
your DFP to anyone, the package is just the medium for you to connect to 
your own data. If you wanted more control you would specify those options like so: 

```{r other-params, eval=FALSE}
options(rdfp.application_name = "MyApp")
options(rdfp.client_id = "012345678901-99thisisatest99.apps.googleusercontent.com")
options(rdfp.client_secret = "Th1s1sMyC1ientS3cr3t")

dfp_auth()
```

```{r auth, include = FALSE}
## I grab the token from the testing directory because that's where it is to be
## found on Travis
token_path <- file.path("..", "tests", "testthat", "rdfp_token.rds")
suppressMessages(dfp_auth(token = token_path, verbose = FALSE))
options_path <- file.path("..", "tests", "testthat", "rdfp_options.rds")
rdfp_options <- readRDS(options_path)
options(rdfp.network_code = rdfp_options$network_code)
```

#### Create an Order

This example uses a test company as an advertiser and yourself as the trafficker, 
to create an order.

```{r eval=FALSE}
request_data <- list('filterStatement'=list('query'="WHERE name = 'TestCompany1'"))
dfp_getCompaniesByStatement_result <- dfp_getCompaniesByStatement(request_data) 

request_data <- list(list(name='TestOrder', 
                          startDateTime=list(date=list(year=2018, month=12, day=1), 
                                             hour=0,
                                             minute=0,
                                             second=0,
                                             timeZoneID='America/New_York'),
                          endDateTime=list(date=list(year=2018, month=12, day=31), 
                                           hour=23,
                                           minute=59,
                                           second=59,
                                           timeZoneID='America/New_York'), 
                          notes='API Test Order', 
                          externalOrderId=99999, 
                          advertiserId=dfp_getCompaniesByStatement_result$id, 
                          traffickerId=dfp_getCurrentUser()$id))
dfp_createOrders_result <- dfp_createOrders(request_data)
```

#### Get Line Items By A Filter

Below is an example of how to get objects by Publishers Query Language (PQL) statement.
The statement is constructed as a list of lists that are nested to emulate
the hierarchy of the XML to be created. The example uses the `dfp_getLineItemsByStatement`
function from the [LineItemService] (https://developers.google.com/doubleclick-publishers/docs/reference/v201802/LineItemService)

```{r}
# retrieve 3 line items that have a status of "DELIVERING"
request <- list('filterStatement'=list('query'="WHERE status='DELIVERING' LIMIT 3"))
resultset <- dfp_getLineItemsByStatement(request, as_df=TRUE)
resultset[,c('orderId', 'id', 'priority', 'deliveryRateType')]
```
